---
format: gfm
knitr:
  opts_chunk:
    echo: false
    comments: "|"
---

```{r init}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

# Getting started

This project uses [`pixi`](https://pixi.sh) to manage the R runtime and
`renv` for R package dependencies.

## Prerequisites

Make sure the following tools are installed on your system:

- [`git`](https://git-scm.com/downloads): To version control the codes
- [`pixi`](https://pixi.sh): Install via `curl -fsSL https://pixi.sh/install.sh | bash`
- [`quarto`](https://quarto.org/docs/download/): Required to compile Quarto documents

For convenience, you may also need [RStudio](https://posit.co/downloads/) or
other IDE installed and running well in your system.

## Reproduction steps

1. **Clone the repository** and enter the directory:

   ```{.bash}
   git clone https://github.com/namakala/inappropriate-acid-suppressor-agent-use
   cd inappropriate-acid-suppressor-agent-use
   ```

2. **Install the pixi environment** (R runtime + `renv`):

   ```{.bash}
   pixi install
   ```

3. **Launch R** with the project environment:

   ```{.bash}
   pixi run R
   ```

   Alternatively, activate a shell with the environment loaded:

   ```{.bash}
   pixi shell
   R
   ```

4. **Restore R packages** (inside the R console):

   ```{.r}
   renv::restore()
   ```

   This reads `renv.lock` and installs all required packages. Restart your R
   session afterwards.

5. **Install tinytex** (needed for PDF output):

   ```{.bash}
   quarto tools install tinytex
   ```

## Data preparation

At this point, you need to export the data as `data.csv` and place it within
the `data/raw` directory. The directory structure *must* look like this:

```{.bash}
data
├── ...
├── raw
│   └── data.csv
└── ...
```

## Running the analysis

Then, you should be able to proceed with:

```{.r}
targets::tar_make()
```

Or from the command line:

```{.bash}
pixi run R -e "targets::tar_make()"
```

This step will read `_targets.R` file, where I systematically draft all of the
analysis steps. Once it's done running, you will find the rendered document
(either in `html` or `pdf`) inside the `draft` directory.

# What's this all about?

This is the functional pipeline for conducting statistical analysis. The complete flow can be viewed in the following `mermaid` diagram:

```{r, results = "asis"}

cat("```mermaid", tar_mermaid(), "```", sep = "\n")

```
