---
title: "Meta-Analysis Interim Report"
format: pdf
metadata-files:
  - _knitr-bib.yml
---

```{r init}

options(scipen = 99)
pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

# Methods

- When funnel plot seemed asymmetrical, doi plot was preferred to avoid subjective selection.
- Copas model selection was performed as a sensitivity analysis to detect and adjust for publication bias.
- Further reading list:
  - https://www.sciencedirect.com/science/article/abs/pii/S0895435609002236
  - https://www.jclinepi.com/article/S0895-4356(08)00348-X/abstract
  - https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1266

\pagebreak

# Meta-analysis on the whole dataset

```{r helper-functions}

catf <- function(msg, ...) {
  sprintf(msg, ...) |> cat()
}

getMetaDetails <- function(meta_object) {

  msg <- capture.output(
    meta:::catmeth(
      meta_object,  
      common          = TRUE,  
      random          = TRUE,   
      print.tau2      = TRUE,
      overall         = TRUE,  
      overall.hetstat = TRUE,  
      backtransf      = FALSE,  
      prediction      = FALSE,  
      print.tau2.ci   = TRUE,
      print.I2        = FALSE,
      func.transf     = meta_object$func.transf,  
      func.backtransf = meta_object$func.backtransf,  
      big.mark        = ",",   
      digits          = 3,  
      digits.tau      = 3,  
      text.tau        = "$\\tau$",   
      text.tau2       = "$\\tau^2$",  
      text.I2         = "$I^2$"
    )
  )

  clean_msg <- msg[-1] %>%
    {gsub(x = ., ":$", ":\n\n")} |>
    paste(collapse = "\n")

  return(clean_msg)

}

printSummary <- function(mod, detail = FALSE) {
  require("meta")

  msg_hetero <- c("$\\tau^2$: %.3f", "$I^2$: %.2f%%", "$H$: %.2f", "Wald's $Q$: %s\n\n") |>
    paste(collapse = "\n- ")

  res <- summary(mod)

  catf(
    "**%s: %.3f [%.3f, %.3f]**  \n",
    res$text.random,
    logit2p(res$TE.random),
    logit2p(res$lower.random),
    logit2p(res$upper.random)
  )
  catf("Number of studies: %d  \n", res$k)
  catf("Number of observations: %s  \n", prettyNum(sum(res$n), big.mark = ","))
  catf("Number of events: %s  \n\n", prettyNum(sum(res$event), big.mark = ","))
  cat("Heterogeneity measures:\n\n")
  catf(
    paste("-", msg_hetero),
    res$tau2,
    res$I2 * 100,
    res$H,
    prettyNum(res$Q[[1]], big.mark = ",")
  )
  if (detail) {
    cat(getMetaDetails(mod))
  }
}

```

```{r meta-summary, results = "asis"}
#| fig-height: 4

funnel_title <- "Publication bias and small-study effects for model: %s"

tar_load(mod_prop)
printSummary(mod_prop, detail = FALSE)

meta::funnel(mod_prop, type = "contour")
title(sprintf(funnel_title, "mod_prop"))

```

```{r meta-summary-doi}
#| fig-height: 4

metasens::doiplot(mod_prop) # Recommended over funnel plot (10.1111/jebm.70063)

```

```{r meta-summary-copas}
#| fig-height: 8

tar_read(mod_copas_prop) %T>% plot() |> summary()

```

\pagebreak


\pagebreak

# Subgroup meta-analysis

```{r subgroup-summary, results = "asis"}

obj_subgroups <- tar_objects(dplyr::contains("mod_subgroup"))

for (obj in obj_subgroups) {
  catf("\n## Model: `%s`\n\n", obj)
  tar_load(obj)
  printSummary(get(obj))
  #meta::funnel(get(obj), type = "contour")
  metasens::doiplot(get(obj))
  title(sprintf(funnel_title, obj))
  cat("\n\n")
  obj_copas <- gsub(x = obj, "mod", "mod_copas")
  tar_load(obj_copas)
  cat("```\n\n")
  lapply(get(obj_copas), summary) |> print()
  cat("```\n\n")
  cat("\\pagebreak")
}

```

# Meta-regression

## Univariate models

```{r metareg-uni-summary, results = "asis"}

obj_metareg_uni <- tar_objects(dplyr::contains("mod_metareg")) %>%
  {.[!grepl(x = ., "_mv")]}

for (obj in obj_metareg_uni) {
  catf("\n### Model: `%s`\n\n", obj)
  tar_load(obj)
  cat("```\n\n")
  summary(get(obj)) |> metafor:::print.summary.rma()
  cat("```\n\n")
  meta::funnel(get(obj))
  title(sprintf(funnel_title, obj))
  cat("\n\n")
  cat("\\pagebreak")
}

```

## Multivariate model

```{r metareg-mv-summary, echo = TRUE}

tar_load(mod_metareg_mv)
summary(mod_metareg_mv)
meta::funnel(mod_metareg_mv)
title(sprintf(funnel_title, "mod_metareg_mv"))

```
